SST_patterns

### 2020-04-07 SST_patterns.Rmd
update
glht

library(tidyverse)
library(multcomp)

@@

# lmod <- lm(mean_intensity ~ mean_dur, data = metrics)
# summary(lmod)
# 
# glht(lmod, linfct = K)

>>>>

library(tidyverse)
library(lubridate)
library(multcomp)
options(scipen = 999)

@@

# anova_func <- function(df){
#   currents_aov <- aov(mean_intensity ~ mean_dur  * site, data = df)
#   return(currents_aov)
# }
# anova_metrics <- anova_func(df = metrics)
# summary(anova_metrics)
# 
# anova <- function(df){
#   currents_aov <- aov(mean_intensity ~ mean_dur  * product, data = df)
#   return(currents_aov)
# }
# anova_metrics <- anova(df = metrics)
# summary(anova_metrics)

lm_coeff <- function(df){
  res <- lm(formula = val ~  , data = df)
  res_coeff <- round(as.numeric(res$coefficient[2]), 2)
}

lm_metrics <- metrics %>% 
  gather(key = "var", value = "val", -c(product:site)) %>% 
  group_by(site, var, product) %>% 
  nest() %>% 
  mutate(slope = purrr::map(data, lm_coeff)) %>% 
  select(-data) %>% 
  unnest()

### define coefficients of linear function directly
K <- diag(length(coef(lm_metrics)))[-1,]
  rownames(K) <- names(coef(lm_metrics))[-1]
K

### set up general linear hypothesis
  glht(lm_metrics, linfct = K)
